---
title: "project115"
author: "Alfonso Vieyra"
date: "3/18/2024"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bayesrules)
library(dplyr)
library(tidyverse)
library(rstanarm)
library(bayesplot)
library(broom.mixed)
library(tidybayes)
vgames_df <- read.csv("./video_games.csv")
```

### Clean data 

```{r}
# reading the data in as a dataframe but then reassign data frame with the 
# variables = review_score, console, length, genres, sales where response 
# is review score

vgames_df <- vgames_df %>% 
         rename(review_score = Metrics.Review.Score, console = Release.Console, 
         length = Length.All.PlayStyles.Average, genres = Metadata.Genres, 
         sales = Metrics.Sales, rating=Release.Rating)

vgames_df <- vgames_df %>% 
  select(review_score, console, length, genres, sales, rating)

head(vgames_df)
```

```{r}
# Changes genres into a single genre
for (row in 1:nrow(vgames_df)) {
  genres <- strsplit(vgames_df$genres[row], split = ",", fixed = TRUE)[[1]]
  if(length(genres) > 0) { 
    i <- sample(length(genres), 1) 
    vgames_df$genres[row] <- genres[i]
  }
}

head(vgames_df)
```



```{r}
colSums(is.na(vgames_df))
```

```{r}
ggplot(vgames_df, aes(x = length, y = review_score)) + 
  geom_point(size = 0.5) + xlim(0,100) + ggtitle(" Game Review Score vs. Game Length")
```

```{r}
ggplot(vgames_df, aes(x = sales, y = review_score)) + 
  geom_point(size = 0.5) + ggtitle(" Game Review Score vs. Game Sales")
```

```{r}
ggplot(vgames_df, aes(x=review_score)) + geom_histogram() + ggtitle("Review Score Histogram")
```

```{r}
ggplot(vgames_df, aes(x=review_score)) + geom_histogram() + facet_wrap(genres ~ ., scales = "free") + ggtitle("Histograms for Genres")
```

```{r}
ggplot(vgames_df, aes(x=review_score)) + geom_histogram() + facet_wrap(console ~ ., scales = "free") + ggtitle("Histograms for Consoles")
```

```{r}
ggplot(vgames_df, aes(x=review_score)) + geom_histogram() + facet_wrap(rating ~ ., scales = "free") + ggtitle("Histograms for Ratings")
```



## Developing an informative prior

Below are 2 data sets and their respective games list that contain review 
scores. They come from a very large media platform that is well known for 
video game reviews and therefore serve as an excellent way to develop some prior 
expectations.

The data sets are from Kaggle where the data scourced is from Metacritic and 
Steam. The Metacritic data set contains a metascore based on journalist reviews and 
a user score based on user reviews. The Steam data set contains only user review scores. 

Link to metacritic data set: 
https://www.kaggle.com/datasets/henrylin03/metacritic-games-user-reviews-and-metascores

Link to steam data set:
https://www.kaggle.com/datasets/andrewmvd/steam-reviews

### Metacritic 

```{r}
# Removing rows that do not feature a recorded review score or is na
metacritic_df <- read.csv("../prior_datasets/metacritic_game_reviews.csv")
metacritic_df <- drop_na(metacritic_df)

# removed rows in metascore that do not have a digit and converted column to 
# integer
metacritic_df <- metacritic_df[metacritic_df$metascore != "tbd", ]
metacritic_df$metascore <- as.integer(metacritic_df$metascore)

# removed rows in user score that do not have a digit and converted column to 
# integer
metacritic_df <- metacritic_df[metacritic_df$userscore != "tbd", ]
metacritic_df$userscore <- as.integer(metacritic_df$userscore)

# convert userscore to scale of 0 - 100 (note:user score 0 - 10 default)
metacritic_df$userscore <- round(metacritic_df$userscore * 10, 0)
```

#### Journalist score

```{r}
ggplot(metacritic_df, aes(x = metascore)) +
  geom_histogram()
```

```{r}
summary(metacritic_df$metascore)
```

```{r}
metacritic_df %>%
  summarise(variance = var(metascore), standard_deviation =  sd(metascore))
```

```{r}
# See platform specific average review ratings
metascore_platforms <- metacritic_df %>%
  group_by(platform) %>%
  summarise(average_platform_metascore = mean(metascore))

summary(metascore_platforms$average_platform_metascore)
```

```{r}
ggplot(metascore_platforms, aes(x = average_platform_metascore)) + 
  geom_histogram(binwidth = 1)
```

#### User score

```{r}
ggplot(metacritic_df, aes(x = userscore)) +
  geom_histogram(binwidth = 10)
```

```{r}
summary(metacritic_df$userscore)
```

```{r}
metacritic_df %>%
  summarise(variance = var(userscore), standard_deviation =  sd(userscore))
```


```{r}
userscore_platforms <- metacritic_df %>%
  group_by(platform) %>%
  summarise(average_platform_userscore = mean(userscore))

summary(userscore_platforms)
```

```{r}
ggplot(metacritic_platforms_user, aes(x = average_platform_userscore)) + 
  geom_histogram(binwidth = 1)
```

### Steam review scores

```{r}
steam_df <- read.csv("../prior_datasets/steam_reviews_dataset.csv")
steam_df <- drop_na(steam_df)
```

```{r}
# Group and add reviews based on positive sentiment
steam_df <- steam_df %>%
  group_by(app_name) %>%
  summarise(score = round((sum(review_score == 1) / n())*100), 0)
```

```{r}
ggplot(steam_df, aes(x = score)) +
  geom_histogram()
```

```{r}
summary(steam_df$score)
```

```{r}
steam_df %>%
  summarise(variance = var(score), standard_deviation =  sd(score))
```

### intercept prior
We see that the average reviews for Metacritic's journalist score and user score 
are approximately 70.84 and 64.19, respectively. Furthermore, Steam's user score 
mean was 72.73. Taking the mean of these respective scores we get a score of 
69.25.

We get a variance of 161.5068	for Metacritics metascore, 207.0729	for 
Metacritic's userscore and 459.8953 for Steam's userscore. The overall mean of 
the variance of these three scores is 276.1583. 

Overall then, our stated prior would include a mean of 69.25 and a variance of 
276.1583. 

**intercept prior**: N(u = 69.25, sigma = 16.618)



```{r}
# Using a Normal Regression
# Priors:
#   Normal(69.25, 16.618) for Beta_0c
#   Vague priors for the other betas
#   Vague prior for sigma
# Model 1: X = genres

vgame_model_1 <- stan_glm(
  review_score ~ genres,
  data = vgames_df, family = gaussian,
  prior_intercept = normal(69.25, 16.618),
  prior = normal(0, 5, autoscale = TRUE),
  prior_aux = exponential(1, autoscale = TRUE),
  chains=4, iter=5000*2, seed=84735)
```

```{r}
mcmc_trace(vgame_model_1)
mcmc_dens_overlay(vgame_model_1)
mcmc_acf(vgame_model_1)
```

```{r}
tidy(vgame_model_1, effects = c("fixed", "aux"),
     conf.int = TRUE, conf.level = 0.95)
```

```{r}
as.data.frame(vgame_model_1) %>%
  mutate(Action = `(Intercept)`,
         Adventure = `(Intercept)` + genresAdventure,
         Educational = `(Intercept)` + genresEducational,
         Racing = `(Intercept)` + `genresRacing / Driving`,
         RPG = `(Intercept)` + `genresRole-Playing (RPG)`,
         Simulation = `(Intercept)` + genresSimulation,
         Sports = `(Intercept)` + genresSports,
         Strategy = `(Intercept)` + genresStrategy) %>%
  mcmc_areas(pars = c("Action", "Adventure", "Educational", "Racing", "RPG",
                      "Simulation", "Sports", "Strategy"))
```


```{r}
# Model 2: X = sales
vgame_model_2 <- stan_glm(
  review_score ~ sales,
  data = vgames_df, family = gaussian,
  prior_intercept = normal(69.25, 16.618),
  prior = normal(0, 5, autoscale = TRUE),
  prior_aux = exponential(1, autoscale = TRUE),
  chains=4, iter=5000*2, seed=84735)
```

```{r}
mcmc_trace(vgame_model_2)
mcmc_dens_overlay(vgame_model_2)
mcmc_acf(vgame_model_2)
```

```{r}
tidy(vgame_model_2, effects = c("fixed", "aux"),
     conf.int = TRUE, conf.level = 0.95)
```

```{r}
vgames_df %>%
  add_fitted_draws(vgame_model_2, n = 100) %>%
  ggplot(aes(x=sales, y=review_score)) +
  geom_point(size=0.5) +
  geom_line(aes(y=.value, group=.draw))
```


```{r}
# Model 3: X = length
vgame_model_3 <- stan_glm(
  review_score ~ length,
  data = vgames_df, family = gaussian,
  prior_intercept = normal(69.25, 16.618),
  prior = normal(0, 5, autoscale = TRUE),
  prior_aux = exponential(1, autoscale = TRUE),
  chains=4, iter=5000*2, seed=84735)
```

```{r}
mcmc_trace(vgame_model_3)
mcmc_dens_overlay(vgame_model_3)
mcmc_acf(vgame_model_3)
```

```{r}
tidy(vgame_model_3, effects = c("fixed", "aux"),
     conf.int = TRUE, conf.level = 0.95)
```

```{r}
vgames_df %>%
  add_fitted_draws(vgame_model_3, n = 100) %>%
  ggplot(aes(x=length, y=review_score)) +
  geom_point(size=0.5) +
  geom_line(aes(y=.value, group=.draw)) + 
  xlim(0,100)
```


```{r}
# Model 4: X = console

vgame_model_4 <- stan_glm(
  review_score ~ console,
  data = vgames_df, family = gaussian,
  prior_intercept = normal(69.25, 16.618),
  prior = normal(0, 5, autoscale = TRUE),
  prior_aux = exponential(1, autoscale = TRUE),
  chains=4, iter=5000*2, seed=84735)
```

```{r}
mcmc_trace(vgame_model_4)
mcmc_dens_overlay(vgame_model_4)
mcmc_acf(vgame_model_4)
```

```{r}
tidy(vgame_model_4, effects = c("fixed", "aux"),
     conf.int = TRUE, conf.level = 0.95)
```

```{r}
as.data.frame(vgame_model_4) %>%
  mutate(DS = `(Intercept)`,
         Wii = `(Intercept)` + `consoleNintendo Wii`,
         PS3 = `(Intercept)` + `consolePlayStation 3`,
         PSP = `(Intercept)` + `consoleSony PSP`,
         X360 = `(Intercept)` + consoleX360) %>%
  mcmc_areas(pars = c("DS", "Wii", "PS3", "PSP", "X360"))
```

```{r}
# Model 5: X = rating

vgame_model_5 <- stan_glm(
  review_score ~ rating,
  data = vgames_df, family = gaussian,
  prior_intercept = normal(69.25, 16.618),
  prior = normal(0, 5, autoscale = TRUE),
  prior_aux = exponential(1, autoscale = TRUE),
  chains=4, iter=5000*2, seed=84735)
```

```{r}
mcmc_trace(vgame_model_5)
mcmc_dens_overlay(vgame_model_5)
mcmc_acf(vgame_model_5)
```

```{r}
tidy(vgame_model_5, effects = c("fixed", "aux"),
     conf.int = TRUE, conf.level = 0.95)
```

```{r}
as.data.frame(vgame_model_5) %>%
  mutate(ratingE = `(Intercept)`,
         ratingM = `(Intercept)` + ratingM,
         ratingT = `(Intercept)` + ratingT) %>%
  mcmc_areas(pars = c("ratingE", "ratingM", "ratingT"))
```

```{r}
# Model 6: X = sales + length
vgame_model_6 <- stan_glm(
  review_score ~ sales + length,
  data = vgames_df, family = gaussian,
  prior_intercept = normal(69.25, 16.618),
  prior = normal(0, 5, autoscale = TRUE),
  prior_aux = exponential(1, autoscale = TRUE),
  chains=4, iter=5000*2, seed=84735)
```

```{r}
mcmc_trace(vgame_model_6)
mcmc_dens_overlay(vgame_model_6)
mcmc_acf(vgame_model_6)
```

```{r}
tidy(vgame_model_6, effects = c("fixed", "aux"),
     conf.int = TRUE, conf.level = 0.95)
```


```{r}
# Model 7: X = genres + console
vgame_model_7 <- stan_glm(
  review_score ~ genres + console,
  data = vgames_df, family = gaussian,
  prior_intercept = normal(69.25, 16.618),
  prior = normal(0, 5, autoscale = TRUE),
  prior_aux = exponential(1, autoscale = TRUE),
  chains=4, iter=5000*2, seed=84735)
```

```{r}
mcmc_trace(vgame_model_7)
mcmc_dens_overlay(vgame_model_7)
mcmc_acf(vgame_model_7)
```

```{r}
tidy(vgame_model_7, effects = c("fixed", "aux"),
     conf.int = TRUE, conf.level = 0.95)
```


```{r}
# Model 8: X = genres + console + genres:console
vgame_model_8 <- stan_glm(
  review_score ~ genres + console + genres:console,
  data = vgames_df, family = gaussian,
  prior_intercept = normal(69.25, 16.618),
  prior = normal(0, 5, autoscale = TRUE),
  prior_aux = exponential(1, autoscale = TRUE),
  chains=4, iter=5000*2, seed=84735)
```

```{r}
mcmc_trace(vgame_model_8)
mcmc_dens_overlay(vgame_model_8)
mcmc_acf(vgame_model_8)
```

```{r}
tidy(vgame_model_8, effects = c("fixed", "aux"),
     conf.int = TRUE, conf.level = 0.95)
```

```{r}
ggplot(vgames_df, aes(y=review_score, x=console, color=genres)) +
  geom_boxplot()
```


```{r}
# Model 9: X = genres + sales
vgame_model_9 <- stan_glm(
  review_score ~ genres + sales,
  data = vgames_df, family = gaussian,
  prior_intercept = normal(69.25, 16.618),
  prior = normal(0, 5, autoscale = TRUE),
  prior_aux = exponential(1, autoscale = TRUE),
  chains=4, iter=5000*2, seed=84735)
```

```{r}
mcmc_trace(vgame_model_9)
mcmc_dens_overlay(vgame_model_9)
mcmc_acf(vgame_model_9)
```

```{r}
tidy(vgame_model_9, effects = c("fixed", "aux"),
     conf.int = TRUE, conf.level = 0.95)
```


```{r}
# Model 10: X = genres + sales + genres:sales
vgame_model_10 <- stan_glm(
  review_score ~ genres + sales + genres:sales,
  data = vgames_df, family = gaussian,
  prior_intercept = normal(69.25, 16.618),
  prior = normal(0, 5, autoscale = TRUE),
  prior_aux = exponential(1, autoscale = TRUE),
  chains=4, iter=5000*2, seed=84735)
```

```{r}
mcmc_trace(vgame_model_10)
mcmc_dens_overlay(vgame_model_10)
mcmc_acf(vgame_model_10)
```

```{r}
tidy(vgame_model_10, effects = c("fixed", "aux"),
     conf.int = TRUE, conf.level = 0.95)
```


```{r}
ggplot(vgames_df, aes(y=review_score, x=sales, color=genres)) +
  geom_point(size=0.5) +
  geom_smooth(method="lm", se=FALSE)
```


```{r}
# Model 11: X = everything
vgame_model_11 <- stan_glm(
  review_score ~ .,
  data = vgames_df, family = gaussian,
  prior_intercept = normal(69.25, 16.618),
  prior = normal(0, 5, autoscale = TRUE),
  prior_aux = exponential(1, autoscale = TRUE),
  chains=4, iter=5000*2, seed=84735)
```

```{r}
mcmc_trace(vgame_model_11)
mcmc_dens_overlay(vgame_model_11)
mcmc_acf(vgame_model_11)
```

```{r}
tidy(vgame_model_11, effects = c("fixed", "aux"),
     conf.int = TRUE, conf.level = 0.95)
```



```{r}
new_game_1 <- data.frame(
  genres = factor("Adventure", levels = c("Action", "Adventure", "Strategy", "Sports")),
  console = factor("Nintendo DS", levels = c("Nintendo DS", "Sony PSP", "PlayStation 3")))
posterior_predictive <- posterior_predict(vgame_model_7, newdata = new_game_1)
predictions <- predict(vgame_model_7, newdata = new_game_1, type = "response")
predicted_score <- mean(posterior_predictive)
simulated_reviewscore <- as.data.frame(posterior_predictive)
ggplot(simulated_reviewscore, aes(x = simulated_reviewscore[[1]])) + 
  geom_density(fill = "blue") +
  labs(x = "Predicted Review Score", title = "Predicted Review Scores for Adventure Game in Nintendo DS")
```


```{r}
new_game_2 <- data.frame(
  genres = factor("Action", levels = c("Action", "Adventure", "Strategy", "Sports")),
  sales = 1 
)

posterior_predictive_2 <- posterior_predict(vgame_model_9, newdata = new_game_2)
predictions_2 <- predict(vgame_model_9, newdata = new_game_2, type = "response")
predicted_score_2 <- mean(posterior_predictive_2)
simulated_reviewscore_2 <- as.data.frame(posterior_predictive_2)
ggplot(simulated_reviewscore_2, aes(x = simulated_reviewscore_2[[1]])) +  
  geom_density(fill = "blue") +
  labs(x = "Predicted Review Score", title = "Predicted Review Scores for Action Game with Sales = 1")
```

```{r}
new_game_3 <- data.frame(
  genres = factor("Sports", levels = c("Action", "Adventure", "Strategy", "Sports")),
  sales = 1,
  console = factor("Sony PSP", levels = c("Nintendo DS", "Sony PSP", "PlayStation 3")),
  length = 10,
  rating = factor("E", levels = c("E", "T", "M"))
)

posterior_predictive_3 <- posterior_predict(vgame_model_11, newdata = new_game_3)
predictions_3 <- predict(vgame_model_11, newdata = new_game_3, type = "response")
predicted_score_3 <- mean(posterior_predictive_3)
simulated_reviewscore_3 <- as.data.frame(posterior_predictive_3)
ggplot(simulated_reviewscore_3, aes(x = simulated_reviewscore_3[[1]])) +  
  geom_density(fill = "blue") +
  labs(x = "Predicted Review Score", title = "Predicted Review Scores for Sports Game with Sales = 1, Rating E, and length 10 minutes using Sony PSP")
```

```{r}
loo4 <- loo(vgame_model_4)
loo7 <- loo(vgame_model_7)
loo11 <- loo(vgame_model_11)

loo_compare(loo4, loo7, loo11)
```

